---
title: "WU Linear Model"
author: "Tania Boror"
date: "4/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94 for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link.

You can import the data directly from a link to its website.  Copy that link to the clipboard by right clicking on Raw Data and then copy link.


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
```

### MODEL 1: SIMS~ARM

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()
```


# Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

```{r}
newdata=data.frame(GRIP=94,ARM=88)
predict(model.1, newdata, interval = "prediction")
```


# now add the model fit to our plot
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

The equation for SIMS explained by ARM is
SIMS = -4.1 + 0.0545 * ARM 


### MODEL 2: SIMS~GRIP
```{r}
basicGG <- ggplot(data,aes(y=SIMS,x=GRIP))
```
##Now add in scatterplot

```{r}
basicGG + geom_point()
```


# Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```

# Inferential  (Build linear model)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
predict(model.2, newdata, interval = "prediction")
```


# now add the model fit to our plot
  
```{r}
basicGG + geom_point() + geom_smooth(method=lm)
``` 

The equation for SIMS explained by GRIP is
SIMS = -4.8 + 0.0545 * GRIP

### MODEL 3 SIMS~ARM+GRIP

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```




# Inferential  (Build linear model)
  
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
predict(model.3, newdata, interval = "prediction")
```

The equation for SIMS explained by ARM+GRIP is
SIMS = -5.43 + 0.037 * ARM + 0.024 * GRIP


```{r}
anova(model.1, model.3)
```

The p-value is 0.000004994; therefore it is very unlikely to occur by chance. We reject the null hypothesis. 

The residual standard error with arm and grip os 1.144 while the residual error in model 1 is 1.226. Since 1.144 is smaller than model 1, we conclude model 3 is the best model. 